Ubiquitous Digital Technologies and Spatial Structure; an update

### 2021-03-26 paper/2_final_submission/tranos_ioannides.Rmd
edits for production

The next step in our analysis is to estimate equation \ref{eq4} for cities in England and Wales for which we were able to access internet speed micro-data.
More specifically, we obtained individual speed internet tests from [broadbandspeedchecker.co.uk](broadbandspeedchecker.co.uk).
This website enables individuals to directly measure their upload and download internet speed.
The results of the tests as well as the geo-location of the users are recorded by the website operator and were provided to us in a fully anonymized manner. More discussion about the nature and the validity of this data can be found in the work of Riddlesden and Singleton [@riddlesden_broadband_2014].
The point nature of these individual level data enables us to aggregate them up to any urban level that we are interested in.
Given that all the above analyses focused on functional definitions of cities, we adopt here a morphological definition of a city or a town for the UK, which enables us to test the effect of internet on smaller areas irrespective of being part of a wider urban agglomeration.
Therefore we aggregate the internet speed data at the level of Built-up Areas (BUA) for England and Wales.
This is a 'bricks and mortar' approach which refers to land which is "irreversibly urban in character" including villages, towns or cities.
Some key characteristics of these areas include: minimum size of $20$ hectares;
areas with less than $200$ meters between them are linked to a single built-up area;
larger built-up areas are separated to smaller sub-divisions of built-up areas [@ons2013; see also @johnston_changing_2014; @johnston2016ethnic for other research applications of BUA].

@@

>>>>

The next step in our analysis is to estimate equation \ref{eq4} for cities in England and Wales for which we were able to access internet speed micro-data.
More specifically, we obtained individual speed internet tests from [broadbandspeedchecker.co.uk](https://www.broadbandspeedchecker.co.uk/).
This website enables individuals to directly measure their upload and download internet speed.
The results of the tests as well as the geo-location of the users are recorded by the website operator and were provided to us in a fully anonymized manner. More discussion about the nature and the validity of this data can be found in the work of Riddlesden and Singleton [@riddlesden_broadband_2014].
The point nature of these individual level data enables us to aggregate them up to any urban level that we are interested in.
Given that all the above analyses focused on functional definitions of cities, we adopt here a morphological definition of a city or a town for the UK, which enables us to test the effect of internet on smaller areas irrespective of being part of a wider urban agglomeration.
Therefore we aggregate the internet speed data at the level of Built-up Areas (BUA) for England and Wales.
This is a 'bricks and mortar' approach which refers to land which is "irreversibly urban in character" including villages, towns or cities.
Some key characteristics of these areas include: minimum size of $20$ hectares;
areas with less than $200$ meters between them are linked to a single built-up area;
larger built-up areas are separated to smaller sub-divisions of built-up areas [@ons2013; see also @johnston_changing_2014; @johnston2016ethnic for other research applications of BUA].

@@

# Acknowledgments {.unnumbered}

We are grateful to many audience members at the 2016 Annual Winter Seminar of the German speaking section of the European
Regional Science Association, the North American Regional Science Council meetings, and Fall 2018 Opportunity and Inclusive
Growth Conference, Federal Reserve Bank of Minneapolis, MN. We are also grateful to Max Nathan for very helpful comments, and to
Esteban Rossi-Hansberg and anonymous reviewers, whose suggestions have not been yet fully incorporated in this version. We are also thankful 
to [broadbandspeedchecker.co.uk](https://www.broadbandspeedchecker.co.uk/) for providing the UK internet speed data.
Naturally, all errors are ours.

### 2021-03-26 paper/2_final_submission/tranos_ioannides.tex
edits for production

The next step in our analysis is to estimate equation \ref{eq4} for
cities in England and Wales for which we were able to access internet
speed micro-data. More specifically, we obtained individual speed
internet tests from \url{broadbandspeedchecker.co.uk}. This website
enables individuals to directly measure their upload and download
internet speed. The results of the tests as well as the geo-location of
the users are recorded by the website operator and were provided to us
in a fully anonymized manner. More discussion about the nature and the
validity of this data can be found in the work of Riddlesden and
Singleton {[}68{]}. The point nature of these individual level data
enables us to aggregate them up to any urban level that we are
interested in. Given that all the above analyses focused on functional
definitions of cities, we adopt here a morphological definition of a
city or a town for the UK, which enables us to test the effect of
internet on smaller areas irrespective of being part of a wider urban
agglomeration. Therefore we aggregate the internet speed data at the
level of Built-up Areas (BUA) for England and Wales. This is a `bricks
and mortar' approach which refers to land which is ``irreversibly urban
in character'' including villages, towns or cities. Some key
characteristics of these areas include: minimum size of \(20\) hectares;
areas with less than \(200\) meters between them are linked to a single
built-up area; larger built-up areas are separated to smaller
sub-divisions of built-up areas {[}69--71{]}.

@@

>>>>

The next step in our analysis is to estimate equation \ref{eq4} for
cities in England and Wales for which we were able to access internet
speed micro-data. More specifically, we obtained individual speed
internet tests from
\href{https://www.broadbandspeedchecker.co.uk/}{broadbandspeedchecker.co.uk}.
This website enables individuals to directly measure their upload and
download internet speed. The results of the tests as well as the
geo-location of the users are recorded by the website operator and were
provided to us in a fully anonymized manner. More discussion about the
nature and the validity of this data can be found in the work of
Riddlesden and Singleton {[}68{]}. The point nature of these individual
level data enables us to aggregate them up to any urban level that we
are interested in. Given that all the above analyses focused on
functional definitions of cities, we adopt here a morphological
definition of a city or a town for the UK, which enables us to test the
effect of internet on smaller areas irrespective of being part of a
wider urban agglomeration. Therefore we aggregate the internet speed
data at the level of Built-up Areas (BUA) for England and Wales. This is
a `bricks and mortar' approach which refers to land which is
``irreversibly urban in character'' including villages, towns or cities.
Some key characteristics of these areas include: minimum size of \(20\)
hectares; areas with less than \(200\) meters between them are linked to
a single built-up area; larger built-up areas are separated to smaller
sub-divisions of built-up areas {[}69--71{]}.

@@

\hypertarget{acknowledgments}{%
\section*{Acknowledgments}\label{acknowledgments}}
\addcontentsline{toc}{section}{Acknowledgments}

We are grateful to many audience members at the 2016 Annual Winter
Seminar of the German speaking section of the European Regional Science
Association, the North American Regional Science Council meetings, and
Fall 2018 Opportunity and Inclusive Growth Conference, Federal Reserve
Bank of Minneapolis, MN. We are also grateful to Max Nathan for very
helpful comments, and to Esteban Rossi-Hansberg and anonymous reviewers,
whose suggestions have not been yet fully incorporated in this version.
We are also thankful to
\href{https://www.broadbandspeedchecker.co.uk/}{broadbandspeedchecker.co.uk}
for providing the UK internet speed data. Naturally, all errors are
ours.
